Constraints on the masses of substructures in $x$ lens galaxies

### 2016-11-17 doc/Paper2/ms.tex
A tad of writing, and two references

% Abstract of the paper
\begin{abstract}
\end{abstract}

@@

\section{The Jackpot}

@@

This work was supported by a Marsden Fast Start grant from the Royal Society of
New Zealand. We also made use of resources provided by the Centre for
eResearch at the University of Auckland.

>>>>

% Abstract of the paper
\begin{abstract}
We present inferences of the lens mass profile and source surface brightness
profile for a selection of galaxy-galaxy gravitational lens systems,
allowing for the possibility of substructures.
In the ``jackpot'' system (SDSSJ0946+1006) we find X,

\end{abstract}

@@

\section{The Jackpot}
\citep{sonnenfeldJackpot}
\citep{vegettiJackpot}

@@

This work was funded by a Marsden Fast Start grant from the Royal Society of
New Zealand.
